Low Complexity Adaptive Sonar Imaging

### 2016-03-03 LCAforActiveSonarImaging/submission/submit1/answer/answer.tex
la2pdf commit - 2016:03:02	18:11:20	(on. 2.mars)
la2pdf commit - 2016:03:03	09:43:51	(to. 3.mars)

We would like to thank the associate editor for his efforts and for his speedy replies to queries from the authors, and reviewers for their thorough and highly relevant comments. Subsequent sections will target each reviewer's comments in detail. We quote in \textit{italic} statements from the reviewers, and provide our replies in ordinary print,

@@

\begin{enumerate}
\item The steering bound $\phi_\mathrm{3dB}$ depends on not just $\beta$, but also on the number of elements $M$ and the element spacing relative to the wavelength $\frac{d}{\lambda}$. 
\begin{enumerate}
\item We have supplied additional info on how the steering is affected by these parameters in appendix C.
\item Equations (12) and (14) only gave the correct results for our system configuration, and were not very intuitive. Appendix C now replace and extends these equations, and we removed them in hope this will make the article easier to read.
\end{enumerate}
\item Various spelling flaws attempted corrected.
\item Appendix C added. Contains information of where source code and media files can be located. Before the article goes to publishing we will make sure that this link is permanent.
\end{enumerate}

>>>>

We would like to thank the associate editor for his efforts and for his speedy replies to queries from the authors, and reviewers for their thorough and highly relevant comments. The following sections mentions some general changes and the reviewer's comments are answered in detail in the next pages. We quote in \textit{italic} statements from the reviewers, and provide our replies in ordinary print.

\begin{enumerate}
\item The steering bound $\phi_\mathrm{3dB}$ depends on not just $\beta$, but also on the number of elements $M$ and the element spacing relative to the wavelength $\frac{d}{\lambda}$. 
\begin{enumerate}
\item We have supplied additional info on how the steering is affected by these parameters in appendix C.
\item Equations (12) and (14) only gave the correct results for our system configuration, and were not very intuitive. Appendix C now replace and extends these equations, and we removed them in hope this will make the article easier to read.
\end{enumerate}
\item Various spelling flaws attempted corrected.
\item Appendix C added. Contains information of where source code and media files can be located. Before the article goes to publishing we will make sure that this link is permanent.
\item Reference to Synnevåg's proceedings article from 2008, ``A low-complexity data-dependent beamformer'' replaced with his 2011 journal article with the same name. We never intended to reference the proceedings article since this work extends his journal version.
\end{enumerate}

@@
